\chapter{Introduction and Background Research}

% You can cite chapters by using '\ref{chapter1}', where the label must
% match that given in the 'label' command, as on the next line.
\label{chapter1}

% Sections and sub-sections can be declared using \section and \subsection.
% There is also a \subsubsection, but consider carefully if you really need
% so many layers of section structure.
\section{Introduction}

<A brief introduction suitable for a non-specialist, {\em i.e.} without using technical terms or jargon, as far as possible. This may be similar/the same as that in the 'Outline and Plan' document. The remainder of this chapter will normally cover everything to be assessed under the `Background Research` criterion in the mark scheme.>

Here is an example of how to cite a reference using the numeric system \cite{parikh1980adaptive}.

This project relies heavily on the use of unstructured text in determining its recommendations. Therefore, methods are required to process this unstructured text to extract meaning, allow for insightful recommendations to be made. The field of natural language processing is chiefly concerned with problems relating to processing natural, unstructured text.


% Must provide evidence of a literature review. Use sections
% and subsections as they make sense for your project.
\section{Literature review}

\subsection{Natural language processing and text vectorization}
- What is natural language processing?
The domain of natural language processing aims to make computers interpret statements written in human languages. \ref{nlpLitReview}
- What is text vectorization?
- Why does it need to be performed?    

\subsection{Recommendation systems}